Graphs, partitioning and you

### 2016-01-31 evolutionaryComputation/2-practical/report.tex
deleted the old bitchiness and added some flavour text

\section{Methodology}
I copied all the code from the previous practical into this new folder.
Then I went onto a delete rage. Most code was deleted except the Experiment
class, this will probably still be useful.

I use git, so it doens't really matter to accidentally delete to much. After
that I changed the data, I removed everything which was useless. Now the file
only contains the connection numbers. This makes parsing the file a lot
easier. I don't want to do advanced pattern matching when I can quickly modify
the file with a few vim macros. (in this case I just did a `30x').

>>>>

\section{Methodology}
This time again I chose to use scala to solve this assignment. I was pleasently
surprised last time by the power of scala's combinators and hope this will be
the case again. I've become quite a fan of the langauge.
